Other metrics

### 2021-03-02 analysis/rev_prototyping/additional_metrics_results.Rmd
updated with fia done

all_di %>% filter(nparts >20) %>% group_by(singletons, dat) %>% summarize(high_proportion_off = mean(mean_po_comparison_percentile > 95))

@@

ggplot(filter(all_di, mean_po_comparison_percentile > 95), aes( mean_po_comparison - mean_po_comparison_95)) +
  geom_histogram() +
  facet_wrap(vars(dat), scales = "free_y")

@@

jk_di <- jk_di_full %>%
  group_by_all() %>%
  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
  ungroup() %>%
  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingeltons_median, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

@@

prop_results <- all_di_with_resamples %>%
 # filter(!singletons) %>%
  group_by(Dataset, resampling) %>%
  summarize(
    skew_high = mean(skew_percentile_excl > 97.5),
    skew_low = mean(skew_percentile < 2.5),
    even_high = mean(simpson_percentile_excl > 97.5),
    even_low = mean(simpson_percentile < 2.5),
    shannon_high = mean(shannon_percentile > 97.5),
    shannon_low = mean(shannon_percentile < 2.5),
    nsingletons_high = mean(nsingletons_percentile_excl > 97.5),
    nsingletons_low = mean(nsingletons_percentile < 2.5),
    po_high = mean(mean_po_comparison_percentile > 97.5),
    po_low = mean(mean_po_comparison_percentile < 2.5)
  ) %>%
  ungroup() %>%
  tidyr::pivot_longer((-c("Dataset","resampling")), names_to = "metric", values_to = "value") %>%
  mutate(ometric = ordered(metric, levels = c("skew_high", "skew_low", "even_low", "even_high", "shannon_low", "shannon_high", "nsingletons_high", "nsingletons_low", "po_high", "po_low")),
         ometric2 = ordered(metric, levels = c("skew_high",  "even_low",  "shannon_low",  "nsingletons_high", "po_high", "skew_low","even_high","shannon_high", "nsingletons_low", "po_low"))) %>%
  mutate(weird_dir = as.numeric(ometric2) > 5)

>>>>

all_di %>% filter(nparts >20) %>% group_by(singletons, dat) %>% summarize(high_proportion_off = mean(mean_po_comparison_percentile_excl > 95))

@@

ggplot(filter(all_di, mean_po_comparison_percentile_excl > 95), aes( mean_po_comparison - mean_po_comparison_95)) +
  geom_histogram() +
  facet_wrap(vars(dat), scales = "free_y")

@@

jk_di <- jk_di_full %>%
  group_by_all() %>%
  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
  ungroup() %>%
  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_median, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_percentile_excl, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

@@

prop_results <- all_di_with_resamples %>%
 # filter(!singletons) %>%
  group_by(Dataset, resampling) %>%
  summarize(
    skew_high = mean(skew_percentile_excl > 97.5),
    skew_low = mean(skew_percentile < 2.5),
    even_high = mean(simpson_percentile_excl > 97.5),
    even_low = mean(simpson_percentile < 2.5),
    shannon_high = mean(shannon_percentile_excl > 97.5),
    shannon_low = mean(shannon_percentile < 2.5),
    nsingletons_high = mean(nsingletons_percentile_excl > 97.5),
    nsingletons_low = mean(nsingletons_percentile < 2.5),
    po_high = mean(mean_po_comparison_percentile_excl > 97.5),
    po_low = mean(mean_po_comparison_percentile < 2.5)
  ) %>%
  ungroup() %>%
  tidyr::pivot_longer((-c("Dataset","resampling")), names_to = "metric", values_to = "value") %>%
  mutate(ometric = ordered(metric, levels = c("skew_high", "skew_low", "even_low", "even_high", "shannon_low", "shannon_high", "nsingletons_high", "nsingletons_low", "po_high", "po_low")),
         ometric2 = ordered(metric, levels = c("skew_high",  "even_low",  "shannon_low",  "nsingletons_high", "po_high", "skew_low","even_high","shannon_high", "nsingletons_low", "po_low"))) %>%
  mutate(weird_dir = as.numeric(ometric2) > 5)
